Sparse Function Space Representation of Neural Networks for Exploration and Retention

### 2023-05-10 paper/main.tex
starting to fill out background

Here, we omit the dependency of the kernel on $n$, and simply use $\MKxx$ to denote the $n \times n$ matrix with $\kappa(\vx_i,\vx_j)$ as the $ij$\textsuperscript{th} entry, computed for all $\vx_i \in\vX$ where $\vX = (\vx_1,\ldots,\vx_n)$. Similarly, $\vk_{\vx i}$ denotes a vector where each $j$\textsuperscript{th} element is $\kappa(\vx_i, \vx_j)$, and $\kappa_{ii} = \kappa(\vx_i, \vx_i)$.

>>>>

%Here, we omit the dependency of the kernel on $n$, and simply use $\MKxx$ to denote the $n \times n$ matrix with $\kappa(\vx_i,\vx_j)$ as the $ij$\textsuperscript{th} entry, computed for all $\vx_i \in\vX$ where $\vX = (\vx_1,\ldots,\vx_n)$. Similarly, $\vk_{\vx i}$ denotes a vector where each $j$\textsuperscript{th} element is $\kappa(\vx_i, \vx_j)$, and $\kappa_{ii} = \kappa(\vx_i, \vx_i)$.
